\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-01 notes/2loopNLSM.tex
A few polishing touches on my sections.

\abstract{ For now, let's put the things we need to check/compute here in the abstract. 
\begin{enumerate}
\item Does our construction manifest all the cuts for the two-loop n-gon?
\item What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
\item How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
\item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
    , \textcolor{cut-color}{\texttt{cut-color}},
    \textcolor{refl-color}{\texttt{refl-color}},and
    \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
    other colors so that we don't have to keep changing colors in
    multiple locations when we want to change diagram color schemes.
    I think I have updated all of the diagrams to use the
    correctly-named color, but haven't changed any of the backing
    colors for the names.}
\end{enumerate}
}

@@

Even beginning at one loop, we encounter classes of cuts that are
difficult to properly define due to hidden non-physical singularities.
The quintessential example of such a ``pathological'' cut is the 3-1
two-particle cut at one loop which hides a bubble-on-external-leg
singularity
\begin{equation}
  \begin{tikzpicture}
\begin{feynman}
\vertex (a1) at (-.8, -0.6) {1};
\vertex (a2) at (-.8, 0.6) {3};
\vertex (a3) at (-1, 0) {2};
\vertex [dot, scale=2](mid1) at (0,0){};
\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
\vertex [dot, scale=2](mid3) at (1,0){};
\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
\vertex (a4) at (1.8, 0) {4};
\diagram{
(mid1) --[ultra thick,](a1),
(mid1) --[ultra thick,](a2),
(mid1) --[ultra thick,](a3),
%(mid1) --[ultra thick,](mid3),
(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
(mid3) --[ultra thick](a4),
};
\end{feynman}
\end{tikzpicture}
\ni
\frac{\delta(\textcolor{cut-color}{k_4^2})}{\textcolor{ucp-color}{s\, k_4^2}}
n \left[
  \begin{tikzpicture}
    \ver{e1}{-1,0};
    \ver{e2}{-0.6,0.4};
    \ver{e3}{-0.3,0.4};
    \ver{i1}{-0.6,0};
    \ver{i2}{-0.3,0};
    \ver{i3}{0,0};
    \ver{i4}{0.8,0};
    \ver{co}{$(i3)!0.5!(i4)$};
    \ver{e4}{1.2,0};
    \draw[ultra thick] (e1)--(i1)--(i2)--(i3) to [out=80,in=100,min distance=0.4cm](i4)--(e4);
    \draw[ultra thick,ucp-color](i1)--(i2)--(i3);
    \draw[ultra thick,cut-color](i4)--(e4);
    \draw[ultra thick] (i3) to [out=-80,in=-100,min distance=0.4cm](i4);
    \draw[ultra thick] (e2) -- (i1);
    \draw[ultra thick] (e3)--(i2);
    \draw[ultra thick,dashed,cut-color] (co)--++(90:0.5);
    \draw[ultra thick,dashed,cut-color] (co)--++(-90:0.5);
  \end{tikzpicture}
  \right]
\end{equation}
in which one of the uncut propagators is set equal to an external
on-shell propagator.  Discussions about how to resolve these types of
singularities can be found in Refs.~\cite{Edison:2022jln,
  Edison:2022smn, Edison:2020uzf, Geyer:2015bja, Bern:2012uf}
\citepls{Minahan}.  In addition to the bubble-on-external-leg cuts,
there is a related class of cuts in which an uncut propagator is set
to zero by an \emph{internal cut condition}, for instance,
\begin{equation*}
  \begin{tikzpicture}
    \pgfmathsetmacro{\ri}{1};
    \pgfmathsetmacro{\re}{0.6};
    \pgfmathsetmacro{\ang}{35};
    \begin{feynman}
      \blob{i1}{\ang:\ri};
      \blob{i2}{180-\ang:\ri};
      \blob{i3}{180+\ang:\ri};
      \blob{i4}{-\ang:\ri};
      \blob{i5}{ $(i1)!0.5!(i2)$ };
      \ver{e1}{45:\ri+\re};
      \ver{e2}{135:\ri+\re};
      \ver{e3}{225:\ri+\re};
      \ver{e4}{-45:\ri+\re};

@@

      \ver{c1}{0:\cl};
      \ver{c2}{\cang:\cl};
      \ver{c3}{2*\cang:\cl};
      \ver{c4}{3*\cang:\cl};
      \ver{ci}{$(i5)!0.5!(i1)$};
      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
      \draw[ultra thick] (e1)--(i1);
      \draw[ultra thick] (e2)--(i2);
      \draw[ultra thick] (e3)--(i3);
      \draw[ultra thick] (e4)--(i4);
      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
      \node[fill=white,circle] (c) at (0,0) {};
  \end{tikzpicture}.
\end{equation*}
Fully resolving both of these problems is beyond the scope of the
current work, so we will simply not impose any constraints that
require handling these type of cuts.

@@

To construct the double-copy theories, we source the cubic
$\mathcal{N}=0$ YM numerators from Ref.~\cite{Bern:2015ooa} (which
additionally satisfies a relaxed form of color-kinematics duality),
and the cubic $\mathcal{N}=4$ sYM representation from the well-known
$n_{\text{DB}} = n_{\text{CB}} = s (st\, A_{\text{tree}})$ \citepls{}.
On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
to directly compute the needed basis cuts in all 3 theories without
relying on a color-dual pion representation.  We find exact agreement
in each of the three theories for both physical cuts.  Since
Ref.~\cite{Carrasco:2023qgz} has already exhaustively explored the
properties of four-point loop amplitudes in these theories, we direct
interested readers there for more information.

\subsection{Two-loop Yang-Mills revisited}
Given the close ties between pion and gluon scattering for trees and
at one loop, the success of a globally color-dual solution for pions
at two loops warrants a reexamination of the two-loop pure Yang--Mills
problem.  As discussed above in \cref{sec:bootstrap}, BDN failed at
finding an off-shell color-dual representation satisfying 7
assumptions, and were forced to develop an on-shell notion of
color-kinematics duality \cite{Bern:2015ooa}.  Thus we must decide
which assumption(s) to break.  From both a motivation and
implementation standpoint, the simplest assumption to break is the
``power-counting'' statement, which we analyze first.

In our labeling of the two loop Jacobi-basis diagrams, shown in
\ace{Figure out fig}, we find that the power counting bound proposed
by Bern, Davies, and Nohle leads to an initial ansatz with 10,000
terms in the double-box, and 9849 terms for the penta-triangle.
Without power counting restrictions, both the double-box and the
penta-triangle ansatz have an ansatz with 10,010 terms each.  Imposing
diagram automorphisms and maximal-cut gauge invariance on the two
basis diagrams, we reduce the number of terms to XX for the
double-box, and YY for the penta-triangle.  The power-counting
restriction of BDN would further reduce these counts to 2232 and 4072.
In Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
imposed using a spanning set of minimal physical cuts, shown in
\cref{fig:ym-spanning}.  Instead of also directly going to the
spanning cuts, we work within the framework of the Method of Maximal
Cuts \citepls{} in order to identify the simplest cut that is in
tension with the kinematic Jacobi relations.

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing
constraints that directly involve such pathological diagrams.  That
leaves us with 14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc} on which to impose
maximal cuts and symmetries. \ace{Do we want the graphs for these?
  Doable in tikz, but would take some time, or I can dump nice-ish
  versions from mathematica}.  Doing so, we are left with AA total
parameters in the unrestricted ansatz and BB total in the
BDN-restricted ansatz.

@@

Proceeding to the next-to-maximal cuts, we continue to avoid BEL
diagrams.  Additionally, now that we have higher-point vertices, we
avoid diagrams in which the higher-point vertex could contain an
off-shell propagator that carries the same momenta as one of the cut
propagators, \eg \ace{Any feedback on how this looks, especially with
  the dashed lines?} \jm{It looks good!  Can you omit the part where the blue lines actually cross?}\ace{Like so?}
\begin{equation*}
  \begin{tikzpicture}
    \pgfmathsetmacro{\ri}{1};
    \pgfmathsetmacro{\re}{0.6};
    \pgfmathsetmacro{\ang}{35};
    \begin{feynman}
      \blob{i1}{\ang:\ri};
      \blob{i2}{180-\ang:\ri};
      \blob{i3}{180+\ang:\ri};
      \blob{i4}{-\ang:\ri};
      \blob{i5}{ $(i1)!0.5!(i2)$ };
      \ver{e1}{45:\ri+\re};
      \ver{e2}{135:\ri+\re};
      \ver{e3}{225:\ri+\re};
      \ver{e4}{-45:\ri+\re};

      \ver{c1}{0:\cl};
      \ver{c2}{\cang:\cl};
      \ver{c3}{2*\cang:\cl};
      \ver{c4}{3*\cang:\cl};
      \ver{ci}{$(i5)!0.5!(i1)$};
      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
      \draw[ultra thick] (e1)--(i1);
      \draw[ultra thick] (e2)--(i2);
      \draw[ultra thick] (e3)--(i3);
      \draw[ultra thick] (e4)--(i4);
      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
      \node[fill=white,circle] (c) at (0,0) {};

  \end{tikzpicture},
\end{equation*}
as it is non-trivial and beyond the scope of this paper to define
exactly what such a cut and cut contribution means.  After discarding
these types of cuts, we are left with 8 unique cut topologies, shown
in \cref{fig:ym-nmc}, to check.  Seven of these next-to-maximal cuts
are consistent with the kinematic Jacobi relations and symmetries.
Interestingly, the ``kissing triangles'' cut,
\begin{equation*}
  \KissingTriangles \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied.

@@

\ace{\sout{I need to check this.  For now it is a standing
    hypothesis:} Checked.  The failure works as stated.} In fact, we can make the
failure extremely precise.  Start with the diagrams shown in the
Jacobi relation from \cref{eq:TwoLoopJacobiOne}: the double-box,
crossed-box, and penta-triangle.  For each of the three diagrams,
write down the most generic parity-even local ansatz involving four
polarizations and six momenta (any combination of external or loop).
Each ansatz will be 10,010 terms initially.  Next impose the symmetry
constraints on each of the three diagrams, leaving 2761 free
parameters on the double-box, 2576 free parameters on the crossed-box,
and 5040 free paramters on the penta-triangle.  Then impose the
``kissing triangle'' next-to-maximal cut, which in the
\emph{non-planar} $t$-$u$ color channel only recieves contributions from the
double-box
\begin{equation}
  \KissingTriangles
  =
  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
  n \left[
    \KTDBContrib{1}{2}{3}{4}
  \right]
  +
  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
  n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
\end{equation}
After imposing this cut, we find that the original Jacobi relation,
\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
\begin{equation}
  \KissingTriangles
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
Thus we have identified the minimal failure state for a
globally-color-dual two-loop Yang--Mills representation: locality,
symmetry, and the ``kissing triangle'' cut are incompatible with the
kinematic Jacobi relations.

>>>>

\abstract{
\ace{I will start working here over the weekendish}

TODO:\\
For now, let's put the things we need to check/compute here in the abstract. 
\begin{enumerate}
\item Does our construction manifest all the cuts for the two-loop n-gon?
\item What is the physics story here? Perturbative corrections to special Galilon, DBI for inflation? 
\item How can bubble on external legs that are zero by IBP inform generalizations beyond pions?
\item \ace{I have defined a \textcolor{ucp-color}{\texttt{ucp-color}}
    , \textcolor{cut-color}{\texttt{cut-color}},
    \textcolor{refl-color}{\texttt{refl-color}}, and
    \textcolor{jacobi-color}{\texttt{jacobi-color}} as aliases for
    other colors so that we don't have to keep changing colors in
    multiple locations when we want to change diagram color schemes.
    I think I have updated all of the diagrams to use the
    correctly-named color, but haven't changed any of the backing
    colors for the names.}
\end{enumerate}
}

@@

Even beginning at one loop, we encounter classes of cuts that are
difficult to properly define due to hidden non-physical singularities.
The quintessential example of such a ``pathological'' cut is the 3-1
two-particle cut at one loop which hides a bubble-on-external-leg
singularity
\begin{equation}
  \begin{tikzpicture}
\begin{feynman}
\vertex (a1) at (-.8, -0.6) {1};
\vertex (a2) at (-.8, 0.6) {3};
\vertex (a3) at (-1, 0) {2};
\vertex [dot, scale=2](mid1) at (0,0){};
\vertex [dot, scale=1.5,hgrey0](mid2) at (0,0){};
\vertex [dot, scale=2](mid3) at (1,0){};
\vertex [dot, scale=1.5,hgrey0](mid4) at (1,0){};
\vertex (a4) at (1.8, 0) {4};
\diagram{
(mid1) --[ultra thick,](a1),
(mid1) --[ultra thick,](a2),
(mid1) --[ultra thick,](a3),
%(mid1) --[ultra thick,](mid3),
(mid1) --[ultra thick,out=60,in=120,min distance=0.4cm](mid3),
(mid1) --[ultra thick,out=-60,in=-120,min distance=0.4cm](mid3),
(mid3) --[ultra thick](a4),
};
\end{feynman}
\end{tikzpicture}
\ni
\frac{\delta(\textcolor{cut-color}{k_4^2})}{\textcolor{ucp-color}{s\, k_4^2}}
n \left[
  \begin{tikzpicture}
    \ver{e1}{-1,0};
    \ver{e2}{-0.6,0.4};
    \ver{e3}{-0.3,0.4};
    \ver{i1}{-0.6,0};
    \ver{i2}{-0.3,0};
    \ver{i3}{0,0};
    \ver{i4}{0.8,0};
    \ver{co}{$(i3)!0.5!(i4)$};
    \ver{e4}{1.2,0};
    \draw[ultra thick] (e1)--(i1)--(i2)--(i3) to [out=80,in=100,min distance=0.4cm](i4)--(e4);
    \draw[ultra thick,ucp-color](i1)--(i2)--(i3);
    \draw[ultra thick,cut-color](i4)--(e4);
    \draw[ultra thick] (i3) to [out=-80,in=-100,min distance=0.4cm](i4);
    \draw[ultra thick] (e2) -- (i1);
    \draw[ultra thick] (e3)--(i2);
    \draw[ultra thick,dashed,cut-color] (co)--++(90:0.5);
    \draw[ultra thick,dashed,cut-color] (co)--++(-90:0.5);
  \end{tikzpicture}
  \right]
\end{equation}
in which one of the uncut propagators is set equal to an external
on-shell propagator.  Discussions about how to resolve these types of
singularities can be found in Refs.~\cite{Edison:2022jln,
  Edison:2022smn, Edison:2020uzf, Geyer:2015bja, Bern:2012uf}
\citepls{Minahan}.  In addition to the bubble-on-external-leg cuts,
there is a related class of cuts in which an uncut propagator is set
to zero by an \emph{internal cut condition}, for instance,
\begin{equation}
  \label{eq:other-path}
  \begin{tikzpicture}
    \pgfmathsetmacro{\ri}{1};
    \pgfmathsetmacro{\re}{0.6};
    \pgfmathsetmacro{\ang}{35};
    \begin{feynman}
      \blob{i1}{\ang:\ri};
      \blob{i2}{180-\ang:\ri};
      \blob{i3}{180+\ang:\ri};
      \blob{i4}{-\ang:\ri};
      \blob{i5}{ $(i1)!0.5!(i2)$ };
      \ver{e1}{45:\ri+\re};
      \ver{e2}{135:\ri+\re};
      \ver{e3}{225:\ri+\re};
      \ver{e4}{-45:\ri+\re};

@@

      \ver{c1}{0:\cl};
      \ver{c2}{\cang:\cl};
      \ver{c3}{2*\cang:\cl};
      \ver{c4}{3*\cang:\cl};
      \ver{ci}{$(i5)!0.5!(i1)$};
      \path let \p1 =(ci) in coordinate (c5) at (\x1,0.2){};
      \draw[ultra thick] (e1)--(i1);
      \draw[ultra thick] (e2)--(i2);
      \draw[ultra thick] (e3)--(i3);
      \draw[ultra thick] (e4)--(i4);
      \draw[ultra thick] (i5)--(i1)--(i4)--(i3)--(i2)--(i6);
      \draw[ultra thick] (i6) to[out=60,in=180-60] (i5);
      \draw[ultra thick] (i6) to[out=-60,in=180+60] (i5);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c1);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c2);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c3);
      \draw[dashed,ultra thick,cut-color] (0,0) -- (c4);
      \draw[dashed,ultra thick,cut-color] (c5) -- ++(90:0.7*\cl);
      \node[fill=white,circle] (c) at (0,0) {};
  \end{tikzpicture}.
\end{equation}
Fully resolving both of these problems is beyond the scope of the
current work, so we will simply not impose any constraints that
require handling these type of cuts.

@@

To construct the double-copy theories, we source the cubic
$\mathcal{N}=0$ YM numerators from Ref.~\cite{Bern:2015ooa} (which
additionally satisfies a relaxed form of color-kinematics duality),
and the cubic $\mathcal{N}=4$ sYM representation from the well-known
$n_{\text{DB}} = n_{\text{CB}} = s^2t\, \atree)$ \citepls{}.
On the other hand, we use the methods of Ref.~\cite{Carrasco:2023qgz}
to directly compute the needed basis cuts in all 3 theories without
relying on a color-dual pion representation.  We find exact agreement
in each of the three theories for both physical cuts.  Since
Ref.~\cite{Carrasco:2023qgz} has already exhaustively explored the
properties of four-point loop amplitudes in these theories, we direct
interested readers there for more information.

\subsection{Two-loop Yang-Mills revisited}
Given the close ties between pion and gluon scattering for trees and
at one loop, the success of a globally color-dual solution for pions
at two loops warrants a reexamination of the two-loop pure Yang--Mills
problem.  As discussed above in \cref{sec:bootstrap}, BDN failed at
finding an off-shell color-dual representation satisfying 7
assumptions, and were forced to develop an on-shell notion of
color-kinematics duality \cite{Bern:2015ooa}.  Thus we must decide
which assumption(s) to break.  From both a motivation and
implementation standpoint, the simplest assumption to break is the
``power-counting'' statement, which we now analyze.

We follow the same general procedure as outlined above, again
identifying the double-box and penta-triangle as the Jacobi basis
graphs and building a generic ansatz for each of their numerators.
Because we are now considering pure Yang--Mills, each monomial in the
local ansatz must consist of five Lorentz scalar dot products instead
of the six for NLSM, and each monomial must be linear in each of the
four external gluon polarizations.  Thus, the ansatz will be built
from terms of the form
\begin{align}
  \pol_1 \cdot k_2, \quad \pol_1 \cdot k_3, \quad& \pol_1 \cdot \ell_1, \quad \pol_1 \cdot \ell_2, \notag \\
  \pol_2 \cdot k_1, \quad \pol_2 \cdot k_3, \quad& \pol_2 \cdot \ell_1, \quad \pol_2 \cdot \ell_2, \notag \\
  \pol_3 \cdot k_1, \quad \pol_3 \cdot k_2, \quad& \pol_3 \cdot \ell_1, \quad \pol_3 \cdot \ell_2,  \\
  \pol_4 \cdot k_1, \quad \pol_4 \cdot k_2, \quad& \pol_4 \cdot \ell_1, \quad \pol_4 \cdot \ell_2, \notag \\
  \pol_1 \cdot \pol_2, \quad \pol_1 \cdot \pol_3, \quad& \pol_1 \cdot \pol_4, \quad \pol_2 \cdot \pol_3, \notag \\
  \pol_2 \cdot \pol_4, \quad& \pol_3 \cdot \pol_4  \notag
\end{align}
in addition to the purely momentum-dependent terms show in \sect{}.
In our labeling of the two loop Jacobi-basis diagrams, shown in
\ace{Figure out fig}, we find that the power counting bound proposed
by Bern, Davies, and Nohle leads to an initial ansatz with 10,000
terms in the double-box, and 9849 terms for the penta-triangle.
Without power counting restrictions, both the double-box and the
penta-triangle ansatz have an ansatz with 10,010 terms each.  Imposing
diagram automorphisms and maximal-cut gauge invariance on the two
basis diagrams, we reduce the number of terms to XX for the
double-box, and YY for the penta-triangle.  The power-counting
restriction of BDN would further reduce these counts to 2232 and 4072.
In Ref.~\cite{Bern:2015ooa}, the unitarity matching constraints were
imposed using a spanning set of minimal physical cuts, shown in
\cref{fig:ym-spanning}.  Instead of also directly going to the
spanning cuts, we work within the framework of the Method of Maximal
Cuts \citepls{} in order to identify the simplest cut that is in
tension with the kinematic Jacobi relations.

@@

Similar to the pion construction in \cref{sec:pions}, we use the
kinematic Jacobi relations to define the numerators for all cubic
graphs in terms of the two basis graphs, including allowing nontrivial
numerators on BEL diagrams.  We will simply avoid imposing constraints
that directly involve such pathological diagrams.  That leaves us with
14 non-pathological cubic diagrams, shown in \cref{fig:ym-mc}, on
which to impose maximal cuts and symmetries.  Doing so, we are left
with AA total parameters in the unrestricted ansatz and BB total in
the BDN-restricted ansatz.

@@

Proceeding to the next-to-maximal cuts, we continue to avoid
pathological diagrams including the newly-appearing type discussed in
\cref{eq:other-path}. After discarding these types of cuts, we are
left with 8 \ace{(maybe a few more to account for dangling trees)}
unique cut topologies, shown in \cref{fig:ym-nmc}, to check.  Seven of
these next-to-maximal cuts are consistent with the kinematic Jacobi
relations and symmetries.  Interestingly, the ``kissing triangles''
cut,
\begin{equation*}
  \KissingTriangles \,,
\end{equation*}
cannot be satisfied by either the unrestricted or the BDN-restricted
ansatz with Jacobi relations and symmetries applied.

@@

In fact, we can make the failure extremely precise.  Start with the
diagrams shown in the Jacobi relation from \cref{eq:TwoLoopJacobiOne}:
the double-box, crossed-box, and penta-triangle.  For each of the
three diagrams, write down the most generic parity-even local ansatz
involving four polarizations and six momenta (any combination of
external or loop).  Each ansatz will be 10,010 terms initially.  Next
impose the symmetry constraints on each of the three diagrams, leaving
2761 free parameters on the double-box, 2576 free parameters on the
crossed-box, and 5040 free paramters on the penta-triangle.  Then
impose the ``kissing triangle'' next-to-maximal cut, which in the
\emph{non-planar} $t$-$u$ color channel only recieves contributions
from the double-box
\begin{equation}
  \KissingTriangles
  =
  \frac{1}{\textcolor{ucp-color}{\ell_1^2}} \
  n \left[
    \KTDBContrib{1}{2}{3}{4}
  \right]
  +
  \frac{1}{\textcolor{ucp-color}{\ell_2^2}} \
  n\left[\KTDBContrib{1}{3}{2}{4}\right] \,.
\end{equation}
After imposing this cut, we find that the original Jacobi relation,
\cref{eq:TwoLoopJacobiOne}, can no longer be satisfied:
\begin{equation}
  \KissingTriangles
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
Thus we have identified the minimal failure state for a
globally-color-dual two-loop Yang--Mills representation: locality,
symmetry, and the kinematic Jacobi relations for just three diagrams
are incompatible with the ``kissing triangle'' cut.
